---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# baseplus

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/baseplus/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/baseplus/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/baseplus/branch/main/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/baseplus?branch=main)
<!-- badges: end -->

Baseplus aims to enhance functionality by developing novel features derived from the foundation of baseR functions.

## Installation
To install the latest development version from [GitHub](https://github.com/poissonconsulting/baseplus)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/baseplus")
```

## Examples
The infix operator `%nin%` returns a logical vector determining if x is NOT present. 
```{r}
library(baseplus)
output <- "x" %nin% c("a", "b", "c")
print(output)
```

The infix operator `%||%` replaces NULL or length of 0 values with a specified replacement value. 
```{r}
library(baseplus)
x <- NULL
x <- x %||% "replacementValue"
print(x)
```

## Inspiration
 - base

## Contribution
Please report any [issues](https://github.com/poissonconsulting/baseplus/issues).
[Pull requests](https://github.com/poissonconsulting/baseplus/pulls) are always welcome.

## Code of Conduct
Please note that the baseplus project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
